Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-20 paper-v1.tex
abstract

Peer-review is a necessary and essential quality control step for scientific publications but lacks proper  incentives. Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected in the timeliness, quality and fairness. Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up a reputational metric. We designed a protocol of smart contracts called Ants-Review that allows authors or editors to issue a bounty for open anonymous peer-reviews. If requirements are met, peer-reviews will be accepted and payed by the issuer proportionally to their quality and  constructiveness. To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.

>>>>

Peer-review is a necessary and essential quality control step for scientific publications but lacks proper  incentives. Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected in the timeliness, quality and fairness. Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation. We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews. If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their quality and value. To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
